\documentclass{article}
\usepackage{amsmath}
\usepackage{biblatex}
\addbibresource{../sources.bib}
\begin{document}

\section*{Review: CUDA-Based Hybrid Genetic Algorithm for Shop Scheduling - Jia Luo, Didier El Baz, 2018}

\item \textbf{Hybrid GA Architecture:} 
\begin{itemize}
    \item Upper Level: Island model divides the population into subpopulations (islands) running in parallel on CUDA thread blocks. Migration is performed between islands to share best individuals.
    \item Lower Level: Fine-grained GA operates within each island at the thread level, with each CUDA thread representing one individual.
\end{itemize}

\item \textbf{CUDA Design:}
\begin{itemize}
    \item Uses CUDA`s two-dimensional thread grid and memory hierarchy (local, shared, global memory) to maximize parallelism and speed.
    \item Fine-grained GA uses local memory for gene-level operations to minimize latency.
    \item Island model uses shared memory for intra-block operations such as elitism and migration.
\end{itemize}

\item \textbf{Genetic Operators Adaptation:}
\begin{itemize}
    \item \textit{Selection:} Modified to tournament selection within a neighborhood grid to accommodate CUDA`s SIMT architecture, limiting global information dependency.
    \item \textit{Crossover:} Single-point crossover between neighboring paired individuals in the grid, executed in parallel.
    \item \textit{Mutation:} Independent random gene mutations suitable for per-thread parallelism.
    \item \textit{Fitness Calculation:} Fully parallelizable, each thread computes its individual`s fitness independently.
\end{itemize}

\item \textbf{Parameter Tuning:}
\begin{itemize}
    \item Medium selection diameter balances diversity and convergence.
    \item Larger island sizes improve performance by balancing exploration and subpopulation convergence.
    \item Migration interval impacts little on performance; wider intervals recommended to reduce overhead.
\end{itemize}

\item \textbf{Setup:}
\begin{itemize}
    \item CPU: Intel Xeon E5640, 2.67 GHz, one core for serial tests; also tested with four-core OpenMP parallelization.
    \item GPU: NVIDIA Tesla K40 with 2880 CUDA cores clocked at 0.745 GHz, 12 GB GDDR5 memory.
    \item Software: CUDA 8.0 framework used for GPU kernel programming; host code in C.
    \item Population size: Fixed at 1024 individuals, limited by maximum CUDA threads per block.
    \item Tested configurations varied island size, selection diameter, and migration interval to optimize performance.
\end{itemize}

\item \textbf{Performance Results:}
\begin{itemize}
    \item Demonstrates superior solution quality compared to classical GAs using roulette wheel selection.
    \item Achieves significant execution time reductions—up to orders of magnitude faster than serial CPU counterparts.
    \item Scalability shown with increased population size leveraging CUDA`s thousands of concurrent threads.
\end{itemize}

\item \textbf{Significance:} This work effectively integrates parallel GA models with CUDA architecture constraints and advantages, achieving an optimized balance between genetic search quality and computational efficiency on GPUs \cite{luo2018acceleration}.


\bibliographystyle{plain}
\bibliography{sources}

\end{document}
